\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

% \usepackage[dvipsnames]{xcolor}

\definecolor{mygray}{gray}{0}

\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kirill Ryzhikov} & Email : \href{mailto:k.ryzhikov@yahoo.com}{k.ryzhikov@yahoo.com}\\
  Github: \href{https://github.com/kryzhikov}{kryzhikov} & Mobile : +44\hspace{0.5ex}7539\hspace{0.5ex}898109 \\
  Telegram: \href{https://t.me/kryzhikov}{@kryzhikov}
\end{tabular*}

\section{Personal Info}
AI-enthusiast, experienced at classical machine learning tasks and more sophisticated modern deep learning approaches, passionate about quantitative finances and DeFi based products.
Looking for quantitative researcher positions for algo-trading, automated market making and liquidity providing.

\textbf{Looking for relocate possibilities, visa sponsorship needed.}






%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeExpSubheading
{\href{https://www.squarepoint-capital.com}{Squarepoint Capital LLP}}{London, UK}
{\textbf{Quantitative Researcher}, intraday equties strategies}{October 2022 - (Present)}
{\skill{Machine Learning} \skill{Deep Learning} \skill{PyTorch} \skill{Boostings} \skill{Finance} \skill{Market Microstructure}\skill{Time-Series}}
\resumeDesc{
  \begin{itemize}
    \item Working on middle frequency strategies.
    \item Researching intraday and daily equities markets alpha.
    \item Performing end-2-end strategies research pipeline.
  \end{itemize}}


\resumeExpSubheading
{\href{https://mynalabs.ai}{Myna Labs}}{San-Francisco, USA (remote)}
{\textbf{Engineer and researcher advisor}, computer vision and signal processing}{November 2021 - (Present, Advisor)}
{\skill{Deep Learning} \skill{PyTorch} \skill{Triton} \skill{CUDA} \skill{Machine Learning} \skill{Time-Series}}
\resumeDesc{
  \begin{itemize}
    \item Working on research of real-time audio driven video generation for different platforms.
    \item Deploying deep learning powered service as server-side and server-less solutions.
    \item Managed to increase server-side solution by \textbf{50\%} and implemented  parallel requests processing.
  \end{itemize}}


\resumeExpSubheading
{\href{https://www.tinkoff.ru/career/it/ml/}{Tinkoff Bank}}{Moscow, Russia}
{\textbf{Machine Learning Researcher}, Several deep learning tasks, computer vision, NLP, signal processing etc.}{March 2020 - Nov. 2021}
{\skill{Deep Learning} \skill{PyTorch} \skill{Triton} \skill{CUDA} \skill{Machine Learning} \skill{SQL}}
\resumeDesc{
  \begin{itemize}
    \item Worked in research department, building cutting-edge banking and not-banking products.
    \item Deploying deep learning models in production, performing internal research, writing publications (see publications part).
    \item Managed to reduce face-parsing data-base size by almost  \textbf{10} times with filtering and postprocessing. Developed AI-chat bot with talking head and presented it at biggest EMEA conference SPIEF.
  \end{itemize}}



\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Moscow State University}{Moscow, Russia}
{Bachelor Degree in Computer Science}{Sept. 2019 - Aug. 2023}
\resumeItemListStart
\resumeItem{Department}
{Department of Mathematical Statistics, Mathematical Finances Laboratory}
\resumeItem{Thesis}
{Developing news-aware event driven trading algorithm}
\resumeItem{GPA}
{4.5/5}
\resumeItemListEnd
\resumeSubheading
{Center Of Mathematical Finances}{Online}
{Quantitative finances}{Sept. 2021 - Aug. 2022}
\resumeItemListStart
\resumeItem{First Year}
{Developing option pricing algorithm, developing HFT-strategy}
\resumeItem{Graduate Program Project}
{Uniswap v3 AMM strategies research}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Publications}
\resumeSubHeadingListStart

\resumeProjSubheading
{\href{https://github.com/kryzhikov/kryzhikov.github.io/blob/main/docs/63allrussmipt.pdf}{63-th All-Russian scientific conference at MIPT}}{Moscow, Russia}
{\skill{Best research paper and project in AI section}}{23 Nov. - 29 Nov. 2020}
\resumeDesc{Presented new State Of The Art approach for facial mimics reenactment from audio and video sources, using Transposed Convolutions and specific audio-signal and mimics representation, resulting end2end real-time talking heads generation service.}


\resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: Python,  C++, CUDA. }
      }\vspace{-7pt}
\item{
            \textbf{Technologies}{: Git, Docker, Linux. }
      }
\vspace{-7pt}
\item{
            \textbf{Knowledge}{: Algorithms, Data Structures, Machine Learning, Deep Learning, CI/CD, Backtesting.}
      }
\resumeSubHeadingListEnd


\section{Other activities}
\resumeSubHeadingListStart

\resumeProjSubheading
{\href{https://algocode.ru/mlwinter2022/}{Tinkoff ML/DL Educational Programs}}{Moscow, Russia}
{\skill{Lecturer, ML/DL course owner, Seminars teacher }}{23 Nov. 2020 - (Present)}
\resumeDesc{Created program for 2 course for students in fields of machine learning and deep learning. Lead team of 4 teacher and 1 managers. 30\% of students later joined tinkoff team as interns.}

\resumeExpSubheading
{\href{https://www.producthunt.com/posts/botify-ai}{Ex-Human, Inc.}}{SF, USA (remote)}
{\textbf{Computer Vision Engineer}, Developing end2end real-time chat bots visualization system}{March 2020 - Nov. 2021}
{\skill{Deep Learning} \skill{PyTorch} \skill{Triton} \skill{CUDA}}
\resumeDesc{
  \begin{itemize}
    \item Took part in developing next generation Ai-ChatBots platform.
    \item Created MVP visual chat bots, that later became production solution.
    \item Managed to increase time spent in app by nearly \textbf{30\%} in comparison with other popular chat-bot apps.
  \end{itemize}}
\resumeSubHeadingListEnd



%-------------------------------------------
\end{document}